%& -job-name=IgPhyML_manual.pdf
\documentclass[11pt, letterpaper]{article}
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage{graphicx} % Add pictures to your document
\usepackage{bm}
\usepackage{tabto}
\usepackage{hyperref}
\usepackage{changepage}
\setlength{\parindent}{10pt}
\usepackage[margin=1.0in]{geometry}
%\usepackage{listings} % Source code formatting and highlighting
%\usepackage{hyperref} % Add a link to your document
\usepackage{hyperref}

\begin{document}
\sloppy
\title{IgPhyML\\A phylogenetic inference package for B cell repertoires}
\author{Kenneth B. Hoehn\\kenneth.hoehn@yale.edu}
\date{August 2019}

\maketitle


\section*{Online documentation}

IgPhyML documentation has moved online:\\ \url{https://igphyml.readthedocs.io}
\\~\\
For the Immcantation suite more broadly:\\
\url{http://immcantation.org}


\section*{References}
Hoehn, K. B., Vander Heiden, J. A., Zhou, J. Q., Lunter, G., Pybus, O. G., \& Kleinstein S. H. (2019) Repertoire-wide phylogenetic models of B cell molecular evolution reveal evolutionary signatures of aging and vaccination. bioRxiv 558825; doi: https://doi.org/10.1101/558825 
\\~\\
Hoehn, K. B., Lunter, G., \& Pybus, O. G. (2017). A phylogenetic codon substitution model for antibody lineages. Genetics, 206(1), 417-427. doi: http://dx.doi.org/10.1534/genetics.116.196303 
\\~\\
\noindent \textbf{IgPhyML} is based on \textbf{codonPhyML}: \url{https://sourceforge.net/projects/codonphyml}\\
Gil, M., Zanetti, M.S., Zoller, S., \& Anisimova A. (2013) CodonPhyML: fast maximum likelihood phylogeny estimation under codon substitution models. Mol Biol Evol. 2013 Jun;30(6):1270-80. doi: 10.1093/molbev/mst034
\\~\\
and \textbf{PhyML}: \url{http://www.atgc-montpellier.fr/phyml}\\
Guindon, S., Delsuc, F., Dufayard J.F., \& Gascuel O. (2009) Estimating maximum likelihood phylogenies with PhyML. Methods Mol Biol. 2009;537:113-37. doi: 10.1007/978-1-59745-251-9\_6

\end{document}


\grid
\grid
\grid
\grid
